We describe the implementation of LessPM, a passwordless password manager
using Rust as a programming language.
While traditional passwords have a long and respectable history, they have
become increasingly vulnerable to attacks such as brute-forcing, phishing, and
keylogging.
\todo[inline]{
  LessPM seeks to address these deficiencies with a sophisticated
  authentication methods, called WebAuthn.
  Through asymmetric cryptography, WebAuthn provides a secure authentication
  experience with the help of user-owned devices such as smartphones or hardware
  authenticator devices.
  This would eliminate the use of traditional passwords.
}
To secure LessPM's passwords on the server, we employ AES-256 and Argon2 for
encryption, WebAuthn's Credential ID, randomly generated salts, and pepper for
key derivation.

We also use Hypertext Transfer Protocol Secure (HTTPS) to secure
communication between client and server and configured Cross-Origin Request
Sharing (CORS).
Additionally, we used an encrypted version of JSON Web Tokens (JWT, RFC7519),
inspired by JSON Web Encryption (JWE, RFC7516), to maintain user authentication
between client requests.

We created a separate client as a visual proof-of-concept to adhere to The
Law of Demeter,
\todo[inline]{
  Ask Jacky whether she is sure about the footnote here, given that it is an
  abstract.
} while the server handles requests and securely stores user data.
This approach offers promising prospects for a passwordless future in digital
security.

This report provides valuable insights into the implementation and potential
benefits of using WebAuthn and a passwordless approach, along with the security
measures employed to protect user data on the server.