Through implementing LessPM, we aimed to create a barebone implementation that
could serve as a reliable Minimal Viable Product (MVP).
However, we recognize that more work is needed to further enhance and compliment
the product.
The related topics to further improve LessPM are listed below and briefly
discussed as a way to highlight potential drawbacks of the current version.

    \begin{enumerate}[label=$\blacktriangleright$]
        \item \textbf{Authorization Headers}
        \newline Even if~\cite{RFC7519} specifies the \texttt{Authorization}
        header as the appropriate place to append the header, in a system
        using WebAuthn it would be better to construct a cookie with similar
        settings as mentioned earlier in the report.
        This is of particular concern as the HTTP framework we used requires
        to specify exposure of the \texttt{Authorization} header in order for
        JavaScript to read it.
        Exposing it to the client entails exposing it to malefactors as well.
        \item \textbf{Hashing the stored password}
        \newline We emphasized and recognized that only constructing a hash
        for the AES key leaves the stored password exposed \textbf{iff} AES
        gets broken or have an unknown zero-day failure.
        Adding some form of hashing for the password before encrypting it would
        serve an exceptional benefit.
        As of thies writing, we are unsure how this hash would be properly
        implemented, given that we have nothing to construct the hash for the
        password.
        \item \textbf{Hardcoded AES for JWT}
        \newline Each JWT is encrypted with the same AES\@.
        This serves as a great treat to the whole system and was implemented
        this way due to the lack of time during the implementation phase.
        In a perfect scenario, we would have applied the same technique for
        the JWT token as for the passwords.
        \item \textbf{Encrypted Passkey}
        \newline The Passkey that gets stored on the user object could be
        beneficial
        to encrypt.
        While the Argon2 hash of the key serves as a great way to require an
        attacker to get access to the codebase as well as the database,
        the passkey could be encrypted with AES and the Credential ID serve
        as part of the key to decrypt it.
        \item \textbf{Attaching connecting IP to JWT}
        \newline We would have liked to attach the connecting IP address to the
        JWT\@.
        Seeing that a JWT token is exposed to the client and then a form of
        session hijacking, attaching an IP address to the token serves as a
        first-line defence in order to avoid exposure unencrypted
        tokens.\footnote{
            This would not work on a mobile device connected to mobile data,
            seeing that the IP address switches between connections.
        }
        \item \textbf{Properly implement JWE}
        \newline During development, we thought that JWTs were encrypted and
        not just signed.
        We discovered the JWEs~\cite{rfc7516} late in the process and these
        were new to us.
        Due to lack of time, we therefore took the shortcut of just
        implementing the encryption process of JWE, not the remaining metadata.
        In the future, we would like to properly implement these and follow
        the standard.
        \item \textbf{Multiple Authenticators}
        \newline In its current implementation, LessPM supports a single
        registered authenticator per username to maintain a focused security
        approach.
        During registration, the server checks the database for an existing
        username similar to the incoming one and aborts the registration
        ceremony if a match is found.
        While WebAuthn permits users to have multiple authenticators, limiting
        this feature in the initial iteration of LessPM helps ensure a more
        controlled security environment.
        As the system evolves, considering addition of support for multiple
        authenticators can be weighed against potential security risks and
        benefits.
        \item \textbf{Return Passwords with Authentication}
        \newline As part of the authentication process, we could make sure
        that the password list is returned with the last request to
        authenticate.
        This would further emphasize security by not exposing passwords in a
        separate end-point.
        On the same note, it would be good to handle the decryption part of
        the JWE better, seeing that a misconfigured cookie sent to this
        endpoint now returns an error.
        Yet another technical debt as a cause of lack of time.
        This is, however, not something that brings the system to a halt,
        rather an error that needs handling.
    \end{enumerate}